Community Embeddings for Facebook Friend Suggestions\\ \thanks{The reported study was partially supported by RFBR grant \textnumero 20-07-00958. The paper was prepared within the framework of the HSE University Project Group Competition 2020-2022.}

### 2020-10-14 paper-ffs.tex
feedback
Opa

Fig. \ref{fig:fb_graphs} shows the graph spring plotted with networkx and nodes colored by community membership after the last iteration of ComE \cite{networkx}. The spring plotted graph structure on Fig. \ref{fig:fb_graphs} suggest, that with embedding dimension $D=4$, more fitting communities are detected than for $D=2$ and $D=128$.

@@

The shortest-embeddings-distance approach is employed, recommending friends to users that have the shortest distance node embeddings over all users (Algorithm \ref{alg:friend_sug}) or only over users in the same community (Algorithm \ref{alg:friend_sug_com}). Users who are already connected are not recommended again.

>>>>

Fig. \ref{fig:fb_graphs} shows the graph spring plotted with networkx and nodes colored by community membership after the last iteration of ComE \cite{networkx}. The spring plotted graph structure on Fig. \ref{fig:fb_graphs} suggests, that with embedding dimension $D=4$, more fitting communities are detected than for $D=2$ and $D=128$.

@@

The shortest-embeddings-distance approach is employed, recommending friends to users who have the shortest distance node embeddings over all users (Algorithm \ref{alg:friend_sug}) or only over users in the same community (Algorithm \ref{alg:friend_sug_com}). Users who are already connected are not recommended again.
